---
title: "Lab 12 - Likelihood Ratio Bootstrap"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lab 12 - Likelihood Ratio Bootstrap}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753ROSAlab12)
```

# Introduction

This package contains a function `mylam` displays histograms of the Log-Likelihood Ratio $log(\lambda)$ and $\bar{y}$ statistics from a given sample. The cut-off region based on a chosen $\alpha$ level is marked on each plot. The data is generated by means of bootstrapping.

# Example

This is an example of the function in action. The following sample will be iterated $10,000$ times in the bootstrap for use in both the Log-Likelihood Ratio $log(\lambda)$ and $\bar{Y}$.

## Sample

```{r}
y <- c(4.5052, 5.4089, 4.8848, 5.0478, 6.9697, 4.4436, 3.8956, 5.9755, 4.6879, 6.1052)
```

## The function: `mylam`

Using $10,000$ iterations of the sample $y$ above with $\alpha = 0.05$, we have

```{r, fig.align = "center", fig.width=7, fig.height=5}
l <- mylam(iter = 10000, y = y, alpha = 0.05)
```

## Other Items

The function can also display other information from the distributions.

```{r}
names(l)
```

```{r}
l$loglamcut
```

```{r}
l$ybarcut
```

```{r}
l$ybarcutest
```

# The Shiny App: `shinyboots`

The package also contains an interactive Shiny app. To access the application, run the following code in an active `R` session.

```{r, eval=FALSE}
shiny::runGitHub(repo = "MATH4753ROSAlab12", username = "brandanrosa", subdir = "inst/shinyboots")
```
